Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
Update manuscript.Rmd

Movement between islands requires caribou to assess the trade-off associated
with swimming. This trade-off can be understood as density-dependent habitat
selection governed by the Ideal Free Distribution [@Morris1987; @Bradbury2015].
Ideal Free Distribution theory predicts a fitness equilibrium: when the density
in a given habitat patch has exceeded the optimum for fitness within that patch,
animals should relocate and settle new habitat patches, so that fitness is equal
across all patches [@Bradbury2015]. Islands act as discrete habitat patches in
this case, but the costs associated with swimming create a trade-off when moving
between patches. For caribou in the Fogo Island archipelago, the role of forage
limitation in animal habitat selection patterns remains unknown, but swimming
between islands may in part be explained by forage limitation and conspecific
competition.

**Individual variation**

>>>>

Movement between islands requires caribou to assess the trade-off associated
with swimming. This trade-off can be understood as density-dependent habitat
selection governed by the Ideal Free Distribution [@Morris1987; @Bradbury2015].
Ideal Free Distribution theory predicts a fitness equilibrium: when the density
in a given habitat patch has exceeded the optimum for fitness within that patch,
animals should relocate and settle new habitat patches, so that fitness is equal
across all patches [@Bradbury2015]. Islands act as discrete habitat patches in
this case, but the costs associated with swimming create a trade-off when moving
between patches. For caribou in the Fogo Island archipelago, the role of forage
limitation in animal habitat selection patterns remains unknown, but swimming
between islands may be at least partially governed by density-dependent habitat selection.
